Predicting complex diseases: performance, robustness and ..utility..(impact?)

### 2017-12-13 3-oracle.Rmd
save

```{r, message=FALSE}
library(tidyverse)
library(bigsnpr)
library(foreach)
celiac2 <- snp_attach("backingfiles/celiacQC_sub1.rds")
CHR <- celiac2$map$chromosome
POS <- celiac2$map$physical.pos
(G <- celiac2$genotypes)
# (G2 <- big_attach("backingfiles/celiacQC_sub1_tripled1.rds"))
# 
# covar.all <- readRDS("backingfiles/PCA2.rds")$u
# 
# n <- nrow(G)
# n.train <- 6e3
ind.HLA <- snp_indLRLDR(CHR, POS, subset(LD.wiki34, ID == "hild12"))
NCORES <- nb_cores()
```

@@

    AUC(S, Y)
  }
doParallel::stopImplicitCluster()
apply(aucs, 1, summary)
```

@@

```{r}
oracles %>% 
  mutate(
    par.causal = factor(map_chr(par.causal, ~paste(.x[1], .x[2], sep = " in ")),
                        levels = c("30 in HLA", paste(3 * 10^(1:3), "in all")))) %>%
  group_by(par.causal, par.dist, par.h2, par.model) %>%
  summarise(AUC_mean = round(mean(AUC), 3),
            AUC_mean_boot = round(boot(AUC, 1e4, mean), 4)) %>%
  print(n = Inf)
```

@@

```{r}
tmp <- oracles_chr6 %>% 
  mutate(
    par.causal = factor(map_chr(par.causal, ~paste(.x[1], .x[2], sep = " in ")),
                        levels = c("30 in HLA", paste(3 * 10^(1:3), "in all")))) %>%
  group_by(par.causal, par.dist, par.h2, par.model) %>%
  summarise(AUC_mean = round(mean(AUC), 4),
            AUC_mean_boot = round(boot(AUC, 1e4, mean), 4)) %>%
  print(n = Inf)
```

>>>>

```{r, message=FALSE}
library(tidyverse)
library(bigsnpr)
library(foreach)
celiac2 <- snp_attach("backingfiles/celiacQC_sub1.rds")
CHR <- celiac2$map$chromosome
POS <- celiac2$map$physical.pos
(G <- celiac2$genotypes)
ind.HLA <- snp_indLRLDR(CHR, POS, subset(LD.wiki34, ID == "hild12"))
NCORES <- nb_cores()
```

@@

    bigstatsr::AUC(S, Y)
  }
doParallel::stopImplicitCluster()
apply(aucs, 1, summary)
```

@@

```{r}
oracles %>% 
  mutate(
    par.causal = factor(map_chr(par.causal, ~paste(.x[1], .x[2], sep = " in ")),
                        levels = c("30 in HLA", paste(3 * 10^(1:3), "in all")))) %>%
  group_by(par.causal, par.dist, par.h2, par.model) %>%
  summarise(AUC_mean = round(mean(AUC), 4),
            AUC_mean_boot = round(boot(AUC), 4)) %>%
  print(n = Inf)
```

@@

```{r}
tmp <- oracles_chr6 %>% 
  mutate(
    par.causal = factor(map_chr(par.causal, ~paste(.x[1], .x[2], sep = " in ")),
                        levels = c("30 in HLA", paste(3 * 10^(1:3), "in all")))) %>%
  group_by(par.causal, par.dist, par.h2, par.model) %>%
  summarise(AUC_mean = round(mean(AUC), 4),
            AUC_mean_boot = round(boot(AUC), 4)) %>%
  print(n = Inf)
```

### 2017-12-13 4-results-simus.Rmd
save

```{r, fig.asp=0.5, out.width="90%", fig.width=15}
p1 <- results3_corr %>%
  myggplot(aes(AUC, percCases10, color = Parameters)) + 
  geom_point(size = 0.6, alpha = 0.5) +
  geom_smooth(aes(linetype = Parameters), method = "lm", se = FALSE, size = 2) +
  theme(legend.key.width = unit(3.5, "line"), 
        legend.direction = "horizontal") + 
  labs(y = "Proportion of cases among top 10% scores")
p2 <- results3_corr %>%
  myggplot(aes(AUC, percCases20, color = Parameters)) + 
  geom_point(size = 0.6, alpha = 0.5) +
  geom_smooth(aes(linetype = Parameters), method = "lm", se = FALSE, size = 2) + 
  labs(y = "Proportion of cases among top 20% scores") +
  theme(legend.position = "none")

@@

ggsave("figures/supp-AUC-corr.pdf", scale = 1/90, width = 1558, height = 737)

with(results3_corr, cor(AUC, percCases10))
with(results3_corr, cor(AUC, percCases20))
```

>>>>

```{r, fig.asp=0.5, out.width="95%", fig.width=16}
p1 <- results3_corr %>%
  myggplot(aes(AUC, percCases10, color = Parameters)) + 
  geom_point(size = 0.6, alpha = 0.5) +
  geom_smooth(aes(linetype = Parameters), method = "lm", se = FALSE, size = 2) +
  theme(legend.key.width = unit(3.5, "line"), 
        legend.direction = "horizontal") + 
  labs(y = "Proportion of cases among top 10% scores")
p2 <- results3_corr %>%
  myggplot(aes(AUC, percCases20, color = Parameters)) + 
  geom_point(size = 0.6, alpha = 0.5) +
  geom_smooth(aes(linetype = Parameters), method = "lm", se = FALSE, size = 2) + 
  labs(y = "Proportion of cases among top 20% scores") +
  theme(legend.position = "none")

@@

ggsave("figures/supp-AUC-corr.pdf", scale = 1/90, width = 1558, height = 737)
```

```{r}
with(results3_corr, cor(AUC, percCases10))
with(results3_corr, cor(AUC, percCases20))
```

### 2017-12-13 paper/draft.tex
save

We make 5 different simulation procedures, summarized in table \ref{tab:simus}. 
..Simulation.. \textnumero1 uses the whole dataset (the 22 chromosomes), a training set of size 6000 and an heritability of 80\%. It compares all methods (see section \ref{sec:methods}) on all other combination of parameters in 5 simulations. The goal of the first simulation is to quickly discard the T-Trees method.
For simulation \textnumero2, we make also vary the heritability (50\% or 80\%) but we don't run the T-Trees method anymore. The goal of the second simulation is to compare all remaining methods, especially to see how well the ``logit-triple'' method works. We run 20 simulations for each combination of parameters.
For simulation \textnumero3, we continue with 80 more simulations (to reach 100 simulations, i.e.\ 5 times more than in \cite{zhou2013polygenic}), but discarding the ``logit-triple'' method and the ``fancy'' model. 
Simulation \textnumero4 consists in 100 simulations of remaining methods and combinations of parameters on a dataset composed of only the chromosome 6. Reducing the number of SNPs aims at increasing the ..polygenicity.. of our simulated models and at ..virtually.. increasing the sample size [REF? DUDBRIDGE?]. 
Finally, simulation \textnumero5 reuses the whole dataset but varying the size of the training set in order to assess how the number of samples affects predictive performance of the PRS and the ``logit-simple'' methods. 100 simulations are run using 300 causal SNPs anywhere on the genome.

@@

In this study, we use two different measures of predictive accuracy. 
First, we use the Area Under the Receiver Operating Characteristic (ROC) Curve (AUC) \cite[]{fawcett2006introduction,hanley1982meaning,lusted1971signal}. In the case of our study, the AUC is the probability that a PRS of a case is greater than the PRS of a control.
This measure indicates how well we can distinguish between cases and controls using PRSs.
As a second measure, we report the percentage of cases in the 10\% and 20\% largest PRSs. This measure indicates how well we can identify high-risk individuals from a higher PRS in screening campaigns.
[COMMENT ON PREVALENCE?]

@@

\subsection{Maximum AUCs}

[MOVE IN SUPMAT AND METHODS]

Assuming that $y \sim N(0, h^2)$, we can estimate the theoretical value of the AUC that can be achieved given the heritability $h^2$ (see ..SupMat..). We report AUCs of 0.8410 and 0.9406 for respectively an heritability of 50\% and 80\%.
% wray2010genetic

@@

@@

@@

Using the penalized logistic regressions, we report AUCs greater than 95\%, which is not obtained by the upper bound of the P+T method in any scenario (Figure \ref{fig:AUC}). Our penalized regression methods consistently provides better predictive performance than the P+T method for all disease architectures tested [ou pas, FIGURE]. Our method is parallelized and requires only less than 10 minutes to run (with 6 physical cores) [TABLE ?FIGURE?]. Moreover, it results in relatively sparse models with no more than 14,000 predictors entering the models even for the linear model of 3000 causal SNPs [TABLE ?FIGURE?].
P+T runs in only a few seconds because we don't consider the GWAS computation as part of the execution time of the method because this is generally executed by others (e.g.\ consortia) and then only the resulting summary statistics are used to construct a PRS.

@@

\newpage
\begin{table}[htbp]
\caption{Summary of all simulations. When there is symbol `-' in a box, it means that the parameters are the same as the ones in the upper box.}
\vspace*{0.5em}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
\hline
Numero of & \multirow{2}{*}{Dataset} & Size of & Causal SNPs & Distribution & \multirow{2}{*}{Heritability} & Simulation & Number of & \multirow{2}{*}{Methods} \\ 
simulation & & training set & (number and location) & of effects & & model & simulations & \\
\hline
\hline
\multirow{4}{*}{1} & \multirow{4}{*}{All 22 chromosomes} & \multirow{4}{*}{6000} & 30 in HLA & \multirow{2.5}{*}{Gaussian} & \multirow{4}{*}{0.8} & \multirow{2.5}{*}{simple} & \multirow{4}{*}{5} & PRS \\
& & & 30 in all & & & & & logit-simple \\
& & & 300 in all & \multirow{1.5}{*}{Laplace} & & \multirow{1.5}{*}{fancy} & & logit-triple \\
& & & 3000 in all & & & & & T-Trees \\
\hline
\multirow{3}{*}{2} & \multirow{3}{*}{-} & \multirow{3}{*}{-} & \multirow{3}{*}{-} & \multirow{3}{*}{-} & \multirow{2}{*}{0.5} & \multirow{3}{*}{-} & \multirow{3}{*}{20} & PRS \\ 
& & & & & \multirow{2.2}{*}{0.8} & & & logit-simple \\
& & & & & & & & logit-triple \\
\hline
\multirow{2}{*}{3} & \multirow{2}{*}{-} & \multirow{2}{*}{-} & \multirow{2}{*}{-} & \multirow{2}{*}{-} & \multirow{2}{*}{-} & \multirow{2}{*}{simple} & \multirow{2}{*}{80} & PRS \\ 
& & & & & & & & logit-simple \\
\hline
\multirow{2}{*}{4} & \multirow{2}{*}{Chromosome 6 only} & \multirow{2}{*}{-} & \multirow{2}{*}{-} & \multirow{2}{*}{-} & \multirow{2}{*}{-} & \multirow{2}{*}{-} & \multirow{2}{*}{100} & \multirow{2}{*}{-} \\ 
& & & & & & & & \\
\hline
\multirow{5}{*}{5} & \multirow{5}{*}{All 22 chromosomes} & 1000 & \multirow{5}{*}{300 in all} & \multirow{5}{*}{-} & \multirow{5}{*}{-} & \multirow{5}{*}{-} & \multirow{5}{*}{100} & \multirow{5}{*}{-} \\ 
& & 2000 & & & & & & \\
& & 3000 & & & & & & \\
& & 4000 & & & & & & \\
& & 5000 & & & & & & \\
\hline
\end{tabular}
\label{tab:simus}
\end{table}

\newpage
\begin{figure}[h]
\centerline{\includegraphics[width=\textwidth]{main-AUC-logit}}
\caption{Mean of AUC over 100 simulations for our penalized logistic regression (``logit-simple'') and the maximum AUC reported with the P+T method (``PRS-max''). Upper (lower) panel is presenting results for effets following a Gaussian (Laplace) distribution. Error bars are representing $\pm 2 \text{SD}$ of $10^5$ non-parametric bootstrap of the mean of AUC. The blue dotted line represents the maximum achievable AUC. [MODEL AND H2]}\label{fig:main-AUC-logit}
\end{figure}

\newpage
\begin{figure}[h]
\centerline{\includegraphics[width=\textwidth]{main-AUC-PRS}}
\caption{Mean of AUC over 100 simulations for ..the three reported PRSs... Upper (lower) panel is presenting results for effets following a Gaussian (Laplace) distribution. Error bars are representing $\pm 2 \text{SD}$ of $10^5$ non-parametric bootstrap of the mean of AUC. The blue dotted line represents the maximum achievable AUC. [MODEL AND H2]}\label{fig:main-AUC-PRS}
\end{figure}

@@

\newpage
\section*{Supplementary Data}

@@

@@

%\begin{figure}[h]
%\centerline{\includegraphics[width=\textwidth]{ttrees}}
%\caption{Results of T-Trees vs penalized logistic regression. \textbf{A.} Timing (in seconds). \textbf{B.} Number of predictors of the model. \textbf{C.} AUC. \textbf{D.} Percentage of cases in the 10\% largest scores.}\label{fig:ttrees}
%\end{figure}

@@

%\begin{figure}[h]
%\centerline{\includegraphics[width=\textwidth]{AUC-corr}}
%\caption{Percentage of cases in the 2 highest deciles of PRSs as a function of AUC.}\label{fig:AUC-corr}
%\end{figure}

>>>>

We make 5 different simulation scenarios, summarized in table \ref{tab:simus}. 
Scenario \textnumero1 uses the whole dataset (the 22 chromosomes), a training set of size 6000 and an heritability of 80\%. It compares all methods (see section \ref{sec:methods}) on all other combination of parameters in 5 simulations. The goal of the first scenario is to quickly discard the T-Trees method.
For scenario \textnumero2, we make also vary the heritability (50\% or 80\%) but we don't run the T-Trees method anymore. The goal of the second scenario is to compare all remaining methods on all models (including the ``fancy'' model), especially to see how well the ``logit-triple'' method works. We run 20 simulations for each combination of parameters.
For scenario \textnumero3, we continue with 80 more simulations (to reach 100 simulations, i.e.\ 5 times more than in \cite{zhou2013polygenic}), but discarding the ``logit-triple'' method and the ``fancy'' model. 
Scenario \textnumero4 consists in 100 simulations of remaining methods and combinations of parameters on a dataset composed of only the chromosome 6. Reducing the number of SNPs aims at increasing the ..polygenicity.. of our simulated models and at ..virtually.. increasing the sample size [REF? DUDBRIDGE?]. 
Finally, scenario \textnumero5 reuses the whole dataset but varying the size of the training set in order to assess how the number of samples affects predictive performance of the PRS and the ``logit-simple'' methods. 100 simulations are run using 300 causal SNPs anywhere on the genome.

@@

In this study, we use two different measures of predictive accuracy. 
First, we use the Area Under the Receiver Operating Characteristic (ROC) Curve (AUC) \cite[]{fawcett2006introduction,hanley1982meaning,lusted1971signal}. In the case of our study, the AUC is the probability that a PRS of a case is greater than the PRS of a control.
This measure indicates how well we can distinguish between cases and controls using PRSs.
As a second measure, we report the percentage of cases in the 10\% and 20\% largest PRSs. This measure indicates how well we can identify high-risk individuals from a higher PRS in screening campaigns.

@@

@@

In results, we use estimates of maximum achievable AUC values for the simulations: 84\% (respectively 94\%) for heritabilities of 50\% (respectively 80\%).

@@

Main simulations corresponds to scenarios 3 to 5 (Table \ref{tab:simus}). They mainly compare our ``simple'' logistic regression to the standard P+T methods in case of a ``simple'' model (only linear effects).

Using the penalized logistic regression, we report AUCs greater than 93\%, nearly reaching the maximum achievable AUC of 94\%, which is not obtained by the upper bound of the P+T method in any scenario (Figure \ref{fig:main-AUC-logit}). Our penalized regression methods consistently provides better predictive performance than the P+T method for all disease architectures tested, excepted sometimes when we simulate 3000 causals SNPs anywhere on the genome, a case where all methods rarely exceeds 65\% of AUC (Figures \ref{fig:main-AUC-logit} and \ref{fig:supp-AUC-logit}).

Our method is parallelized and requires only less than 10 minutes to run (with 6 physical cores) [TABLE ?FIGURE?]. Moreover, it results in relatively sparse models with no more than 14,000 predictors entering the models even for the linear model of 3000 causal SNPs [TABLE ?FIGURE?].

@@

P+T runs in only a few seconds because we don't consider the GWAS computation as part of the execution time of the method because this is generally executed by others (e.g.\ consortia) and then only the resulting summary statistics are used to construct a PRS.

@@

\newpage
\begin{table}[htbp]
\caption{Summary of all simulations. When there is symbol `-' in a box, it means that the parameters are the same as the ones in the upper box.}
\vspace*{0.5em}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
\hline
Numero of & \multirow{2}{*}{Dataset} & Size of & Causal SNPs & Distribution & \multirow{2}{*}{Heritability} & Simulation & Number of & \multirow{2}{*}{Methods} \\ 
scenario & & training set & (number and location) & of effects & & model & simulations & \\
\hline
\hline
\multirow{4}{*}{1} & \multirow{4}{*}{All 22 chromosomes} & \multirow{4}{*}{6000} & 30 in HLA & \multirow{2.5}{*}{Gaussian} & \multirow{4}{*}{0.8} & \multirow{2.5}{*}{simple} & \multirow{4}{*}{5} & PRS \\
& & & 30 in all & & & & & logit-simple \\
& & & 300 in all & \multirow{1.5}{*}{Laplace} & & \multirow{1.5}{*}{fancy} & & logit-triple \\
& & & 3000 in all & & & & & T-Trees \\
\hline
\multirow{3}{*}{2} & \multirow{3}{*}{-} & \multirow{3}{*}{-} & \multirow{3}{*}{-} & \multirow{3}{*}{-} & \multirow{2}{*}{0.5} & \multirow{3}{*}{-} & \multirow{3}{*}{20} & PRS \\ 
& & & & & \multirow{2.2}{*}{0.8} & & & logit-simple \\
& & & & & & & & logit-triple \\
\hline
\multirow{2}{*}{3} & \multirow{2}{*}{-} & \multirow{2}{*}{-} & \multirow{2}{*}{-} & \multirow{2}{*}{-} & \multirow{2}{*}{-} & \multirow{2}{*}{simple} & \multirow{2}{*}{80} & PRS \\ 
& & & & & & & & logit-simple \\
\hline
\multirow{2}{*}{4} & \multirow{2}{*}{Chromosome 6 only} & \multirow{2}{*}{-} & \multirow{2}{*}{-} & \multirow{2}{*}{-} & \multirow{2}{*}{-} & \multirow{2}{*}{-} & \multirow{2}{*}{100} & \multirow{2}{*}{-} \\ 
& & & & & & & & \\
\hline
\multirow{5}{*}{5} & \multirow{5}{*}{All 22 chromosomes} & 1000 & \multirow{5}{*}{300 in all} & \multirow{5}{*}{-} & \multirow{5}{*}{-} & \multirow{5}{*}{-} & \multirow{5}{*}{100} & \multirow{5}{*}{-} \\ 
& & 2000 & & & & & & \\
& & 3000 & & & & & & \\
& & 4000 & & & & & & \\
& & 5000 & & & & & & \\
\hline
\end{tabular}
\label{tab:simus}
\end{table}

\newpage
\begin{figure}[h]
\centerline{\includegraphics[width=\textwidth]{main-AUC-logit}}
\caption{Scenario \textnumero3. Mean of AUC over 100 simulations for our penalized logistic regression (``logit-simple'') and the maximum AUC reported with the P+T method (``PRS-max''). Upper (lower) panel is presenting results for effets following a Gaussian (Laplace) distribution. Error bars are representing $\pm 2 \text{SD}$ of $10^5$ non-parametric bootstrap of the mean of AUC. The blue dotted line represents the maximum achievable AUC. [MODEL AND H2]}\label{fig:main-AUC-logit}
\end{figure}

\newpage
\begin{figure}[h]
\centerline{\includegraphics[width=\textwidth]{main-AUC-PRS}}
\caption{Scenario \textnumero3. Mean of AUC over 100 simulations for ..the three reported PRSs... Upper (lower) panel is presenting results for effets following a Gaussian (Laplace) distribution. Error bars are representing $\pm 2 \text{SD}$ of $10^5$ non-parametric bootstrap of the mean of AUC. The blue dotted line represents the maximum achievable AUC. [MODEL AND H2]}\label{fig:main-AUC-PRS}
\end{figure}

\newpage
\begin{figure}[h]
\centerline{\includegraphics[width=\textwidth]{main-AUC-ntrain}}
\caption{Scenario \textnumero5. Mean of AUC over 100 simulations for ..the three reported PRSs... and the simple logistic regression as a function of the training size. This results are for an additive model with 300 causal SNPs sampled anywhere on the genome. Upper (lower) panels are presenting results for an heritability of 0.5 (0.8) and left (right) panels are presenting results for effets following a Gaussian (Laplace) distribution. Error bars are representing $\pm 2 \text{SD}$ of $10^5$ non-parametric bootstrap of the mean of AUC. The blue dotted line represents the maximum achievable AUC. [MODEL AND H2]}\label{fig:main-AUC-ntrain}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
\section*{Supplementary Materials}

@@

\subsection*{Maximum AUCs} \label{sec:auc-max}

We used three different ways to estimate the maximum achievable AUC for our simulations.
First, we used the estimation from equation (3) of \cite{wray2010genetic}. For a prevalence fixed at 30\% and an heritability of 50\% (respectively 80\%), the approximated theoretical values of AUC are 84.1\% (respectively 93.0\%). Note that this approximation is reported to be less accurate for high heritabilities.
Secondly, if we assume that the genetic part of the liabilities $y \sim N(0, h^2)$, we can estimate the theoretical value of the AUC that can be achieved given the heritability $h^2$ through Monte Carlo simulations. We report AUCs of 84.1\% and 94.1\% for respectively an heritability of 50\% and 80\%. [HOW TO ADD ERROR? I HAVE SUMMARY()]
Thirdly, we reproduce the exact same procedure of simulations and, for each combination of parameters (Table \ref{tab:simus}), we estimate the AUC of the ``oracle'', i.e.\ the true simulated genetic part of the liabilities though 100 replicates. For every combination of parameters, AUC of oracles are comprised between 83.2\% and 84.2\% for an heritability of 50\% and between 93.2\% and 94.1\% for an heritability of 80\%.
Given all these estimates of the maximal achievable AUC and for the sake of simplicity, we report maximum AUCs of 84\% (respectively 94\%) for heritabilities of 50\% (respectively 80\%) whatever are the parameters of the simulation.

\newpage

@@

\newpage
\begin{figure}[h]
\centerline{\includegraphics[width=\textwidth]{supp-AUC-logit-fancy}}
\caption{[COPY FOR H2=0.5 \& MODEL FANCY]}\label{fig:supp-AUC-logit-fancy}
\end{figure}

\newpage
\begin{figure}[h]
\centerline{\includegraphics[width=\textwidth]{supp-AUC-PRS-fancy}}
\caption{[COPY FOR H2=0.5 \& MODEL FANCY]}\label{fig:supp-AUC-PRS-fancy}
\end{figure}

@@

\newpage
\begin{figure}[h]
\centerline{\includegraphics[width=\textwidth]{supp-ttrees}}
\caption{[T-TREES 3 PLOTS - H2=0.8]}\label{fig:supp-ttrees}
\end{figure}

\newpage
\begin{figure}[h]
\centerline{\includegraphics[width=\textwidth]{supp-triple}}
\caption{[TRIPLE 3 PLOTS - H2=0.8]}\label{fig:supp-triple}
\end{figure}

\newpage
\begin{figure}[h]
\centerline{\includegraphics[width=\textwidth]{supp-AUC-triple}}
\caption{[TRIPLE ONLY AUC - H2=0.5]}\label{fig:supp-AUC-triple}
\end{figure}

\newpage
\begin{figure}[h]
\centerline{\includegraphics[width=\textwidth]{supp-AUC-chr6}}
\caption{Scenario \textnumero4. Boxplots of AUC over 100 simulations for ..the three reported PRSs... and the simple logistic regression.
Vertical panels represents different number of causal SNPs and their location (``all'': anywhere on the genome; ``HLA'': only in the HLA region). Horizontal panels are presenting results for effets following a Gaussian or Laplace distribution and an heritability of 0.5 or 0.8. The blue dotted line represents the maximum achievable AUC. [MODEL AND H2]}\label{fig:supp-AUC-chr6}
\end{figure}

\newpage
\begin{figure}[h]
\centerline{\includegraphics[width=\textwidth]{supp-AUC-corr}}
\caption{Scenario \textnumero3. Comparison of different predictive measures. Correlation is greater than 98\%.[ADD]}\label{fig:supp-AUC-corr}
\end{figure}
